Verifying Demonstrations

### 2018-02-19 paper/DB-anon-cred.tex
Changes from k to k+1 rounds

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
        \ceil{\log_2 q}\)} \\

@@

    % null
    & \(\ProtoSendLeft{b_i}\)
    & \(b_i\gets b\), random delay \\

@@

The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.
On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
adversary to buffer the responses from the prover.
However, in the worst case, the \ac{DBMF} adversary will be detected in the 
first round, since he cannot buffer any response from the prover.
After the first round though, the adversary knows \(b\) and can get those 
requests as quickly as possible from the prover.
By repeating the protocol we decrease this probability.

>>>>

    % null
    &
    & Prepare \(B\in \bin^{k+l}\),
    \\

    % null
    &
    & with \(k\) bits set to \(b\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < k+l\)} 
    \\

@@

    % null
    & \(\ProtoSendLeft{b_i}\)
    & \(b_i\gets B[i]\)
    \\

@@

The \ac{DB} phase protects against distance fraud.
\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with 
\(r_i\).

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(k+l < 2k\) challenges.
Thus the prover reveals the \(k\) bits of either \(s_0\) or \(s_1\) and only 
\(l\) bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
then relay that challenge to the prover to receive the correct \(r_i\) --- this 
relay will be detected.
